Learning to extend a Cybersecurity Knowledge Graph

### 2021-03-09 CyberKGX/main.tex
CyberKG prior to significant rewrite.

\begin{abstract}
It has been shown that malicious model training code can augment sensitive training data with specially-crafted samples to enable later exfiltration of the sensitive data by an attacker who has black-box access to the completed model, but no direct access to the sensitive training data. \cite{DBLP:journals/corr/abs-1709-07886}  This is known as a Covert Channel for machine learning models.  It has also been shown an attacker can infer whether a specific sample was included in the training set for a black-box model if the attacker has knowledge of the model's structure or can generate models with similar structure. \cite{DBLP:journals/corr/ShokriSS16}  This is known as Membership Inference on machine learning models.  We demonstrate that a variation of the Membership Inference `attack' can be used to detect whether a given machine learning model may have a covert channel.  We review some performance factors of the detector, and discuss how performance is directly related to model capacity and sparsity of the sensitive and maliciously-crafted data.
\end{abstract}

>>>>

\begin{abstract}
\input{abstract}
\end{abstract}
